%% ----------------------------------------------------------------------
%% START OF FILE
%% ----------------------------------------------------------------------
%% 
%% Filename: ch06-bibliography.tex
%% Author: Fred Qi
%% Created: 2012-12-26 13:11:58(+0800)
%% 
%% ----------------------------------------------------------------------
%%% CHANGE LOG
%% ----------------------------------------------------------------------
%% Last-Updated: 2012-12-26 13:37:34(+0800) [by Fred Qi]
%%     Update #: 6
%% ---------------------------------------------------------------------
%\bibliographystyle{gbt7714-2005}
%\bibliography{refs}
%\chapter{参考文献}
\begin{thebibliography}{99}
    %\label{cha:bibliography}
    %\bibliographystyle{gbt7714-2005}
    %\bibliography{refs}
    \bibitem{ref1}J. Kammerl, N. Blodow, R. B. Rusu, et al. ``Real-time compression of point cloud streams," IEEE International Conference on Robotics and Automation, 2012, pp. 778-785.
    \bibitem{ref2}S. Schwarz et al. "Emerging MPEG Standards for Point Cloud Compression," in IEEE Journal on Emerging and Selected Topics in Circuits and Systems, 2019, March, vol. 9, no. 1, pp. 133-148.
    \bibitem{ref3}AVS点云编码需求与技术讨论组. AVS点云编码需求与技术分析报告V0.1[C]// AVS\_ N2643，第 68 次会议.中国青岛，2019年3月.
    \bibitem{ref4}C.Cao, M.Preda, and T.Zaharia. ``3D Point Cloud Compression: A Survey". In The 24th International Conference on 3D Web Technology. Association for Computing Machinery, New York, NY, USA, 1–9.
    \bibitem{ref5}Lasserre S. A common dynamic OBUF class for octree and TriSoup, document m60697[R]. Mainz: ISO/IEC JTC1/SC29/WG7 Oct.2022.
    \bibitem{ref6}Lasserre S. Part 1 Improving TriSoup: summary, results and perspective, document m59288[R]. Online: ISO/IEC JTC1/SC29/WG7 Apr.2022.
    \bibitem{ref7}Lasserre S. Part 2 Fixes and simplifications, document m59289[R]. Online: ISO/IEC JTC1/SC29/WG7 Apr.2022.
    \bibitem{ref8}Lasserre S. Part 3 Adding a residual for the centroid vertex, document m59290[R]. Online: ISO/IEC JTC1/SC29/WG7 Apr.2022.
    \bibitem{ref9}Lasserre S. Part 4 Vertex Quantization, document m59291[R]. Online: ISO/IEC JTC1/SC29/WG7 Apr.2022.
    \bibitem{ref10}Lasserre S. Part 5 Improved rendering from triangles, document m59292[R]. Online: ISO/IEC JTC1/SC29/WG7 Apr.2022.
    \bibitem{ref11}Lasserre S. Part 6 Compression of vertex presence flag and vertex position, document m59292[R]. Online: ISO/IEC JTC1/SC29/WG7 Apr.2022.
    \bibitem{ref12}MPEG 3D Graphics Coding, “G-PCC 2nd Edition codec descriptio”, ISO/IEC JTC 1/SC 29/WG 7 N00423, December 2022.
    \bibitem{ref13}J. Jin, G. Li, Y. Shao, F. Song and R. Zhang, "An Improved Coarse-To-Fine Motion Estimation Scheme For Lidar Point Cloud Geometry Compression," 2021 IEEE International Conference on Multimedia \& Expo Workshops (ICMEW), Shenzhen, China, 2021, pp. 1-6, doi: 10.1109/ICMEW53276.2021.9456018.
    \bibitem{ref14}Pierdicca R, Paolanti M, Matrone F, et al. Point cloud semantic segmentation using a deep learning framework for cultural heritage[J]. Remote Sensing, 2020, 12(6): 1005.
    \bibitem{ref15} De Pace F, Gorjup G, Bai H, et al. Leveraging Enhanced Virtual Reality Methods and Environments for Efficient, Intuitive, and Immersive Teleoperation of Robots[C]//2021 IEEE International Conference on Robotics and Automation (ICRA). vienna: IEEE, 2021: 12967-12973.
    \bibitem{ref16}Cao C, Preda M, Zakharchenko V, et al. Compression of sparse and dense dynamic point clouds methods and standards[J]. Proceedings of the IEEE, 2021, 10%(9):1537-1558.
    \bibitem{ref17}MPEG 3DG. G-PCC test model v13 user manual, document w20020[R]. Online: ISO/IEC JTC1/SC29/WG07,2021.
    \bibitem{ref18}Kathariya B, Li L, Li Z, et al. Scalable point cloud geometry coding with binary tree embedded quadtree[C]//2018 IEEE International Conference on Multimedia and Expo (ICME). San Diego:IEEE, 2018: 1-6.
    \bibitem{ref19}3D Graphics, Point Cloud Compression Test Model for Category 1 v1, document w17340[R]. Gwangju: ISO/IEC JTC1/SC29/WG11, Jan. 2018.
    \bibitem{ref20}Gao Z, Flynn D, Tourapis A, et al. Using L1 norm for nearest neighbour search in Prediction and Lifting schemes, document m51011[R]. Geneva: ISO/IEC JTCI/SC29/WG11, Oct. 2019.
    \bibitem{ref21}R. L. de Queiroz, P. A. Chou. Compression of 3D point clouds using a region-adaptive hierarchical transform[J]. IEEE Transactions on Image Processing, 2016, 25(8): 3947-3956
    \bibitem{ref22}Konashkova A M. Modified skala's plane tested algorithm for line-polyhedron intersection[J]. 2015.
    \bibitem{ref23}MPEG 3D Graphics coding, ``Common Test Conditions for G-PCC," ISO/IEC JTC1/SC29/WG7, 140th MPEG meeting, Mainz, Novemberr 2022.
\end{thebibliography}
%% ----------------------------------------------------------------------
%%% END OF FILE 
%% ----------------------------------------------------------------------